### 2014-11-12 language.tex
spacing, ref

\paragraph{SSSP Example}
To make these ideas concrete, we present a simple
program: the single source shortest path program~(SSSP). Later in the paper, we
add coordination facts to improve the execution of the program.

@@

\begin{dblfig}[ht]
\begin{center}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest2}}
  \hspace{0.4cm}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest3}}
  \hspace{0.4cm}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest8}}
\end{center}
\scap{fig:shortest_path_program}{Graphical representation of the SSSP program. Figure (a) represents the
   program after propagating initial distance at node \texttt{@1}, followed by
   Figure (b) where the first rule is applied in node \texttt{@3}. Figure (c)
   represents the state of the final program, where all the shortest paths
   have been computed.}
\end{dblfig}

>>>>

\paragraph{SSSP Example}\label{sect:ssspex}
To make these ideas concrete, we present a simple
program: the single source shortest path program~(SSSP). Later in the paper, we
add coordination facts to improve the execution of the program.

@@

\begin{dblfig}
\begin{center}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest2}}
  \hspace{0.4cm}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest3}}
  \hspace{0.4cm}
  \subfloat[]{\includegraphics[width=0.3\textwidth]{figures/shortest8}}
\end{center}
\scap{fig:shortest_path_program}{Graphical representation of the SSSP program. (a) represents the
   program after propagating initial distance at node \texttt{@1}, followed by
   (b) where the first rule is applied in node \texttt{@3}. (c)
   represents the state of the final program, where all the shortest paths
   have been computed.}
\end{dblfig}
